Since the project is solely a web-based application, we do not require any hardware, but computers connected to the high-speed Internet would be mandatory. Any testing in this project will be implemented on these devices. In light of lab space, due to the Covid-19 situation, in the beginning phase of this project, we do not plan to meet physically in-person. All meetings in this phase is transitioned to virtual on Discord platform. In case the pandemic is officially under control and there is no possibility of infection endangering team members' health and wellness, the UTA's laboratory located in Room 208, 202, and 203 on the second floor of the Engineering Research Building (ERB) will be used for holding any in-person meeting. For this project particularly, we will need the domain name for the website. There are multiple domain registrars that offer the domain name at low cost per month or per year. Once the website is fully or almost done, we will choose the most appropriate domain name from the reliable provider. Besides, the database plays a key role in this project. It would be ideal that UTA can give us access to the CSE department database in order to build the most practical and up-to-date application. Otherwise, we plan to simulate our own database to solely serve the purpose of developing this project. It may take a considerable effort to build the close-to-real-life database, but it will be free. Additionally, we also require the web hosting. Many reputable companies, such as AWS, Microsoft, and Google, provide several packages for hosting the website. The price may vary depending on the website's expectations and goals. We plan to have the special meeting thoroughly discussing this issue when it is appropriate. By the same token, we need the web design software tools for this project. Currently, we plan to use the open-source framework, which is also free. At the end of this project, it is necessary for the team to prepare a poster introducing the project. The plotter printer is available at multiple locations on campus that can fulfil this task. 