%%%%%%%%%%%%%%%%%%%%%%%%
% To cite something, use the \cite command with the name of the bibtex entry in the curly braces.
% It will determine which reference number it is and insert that number where the \cite command is.
% e.g. \cite{Rubin2012}

According to Dr. Yusuff in his peer-reviewed article "Does personalized goal setting and study planning improve academic performance and perception of learning experience in a developing setting?", the goal setting and study planning contributes substantially to the academic performance \cite{YUSUFF2018232}. With this in mind, the comprehensive academic plan from the beginning of college life is essential for students to understand their expectations, interests, and future opportunities. Following this, the purpose of this project is to help students perform their academy at the highest standard. Also, it aims to assist the Department of Advisors in eliminating paperwork and optimizing the advising process. The Interactive Degree Planner allows students to log in using their netIDs. The web page will display the the list of courses that allows user to drag and drop desired item to each semester. However, the course option is only available when its pre-/co-requisite requirements are fulfilled. As long as the course is added into the semester box, the total hours/credits taken that semester will be accordingly updated. The website is expected to assist students to achieve better acknowledgement about their career paths since it provides visualization and interaction, which is scientifically proved as "an excellent way to learn and master complex systems" \cite{bobek_creating_2016}.
With respect to the currently existing application that share the similar ideas with this project, Prepler is the popular web-based degree planner among many colleges \cite{prepler_prepler_nodate}. It is free for basic feature and presents a simple interface. Ellucian Degree Works is the more advanced application compared to Prepler, which offers services in wide range of field from education to business \cite{noauthor_unifying_nodate}. Since Ellucian's application is overloaded with several functionalities using latest technology, this may impact negatively in user experience \cite{noauthor_improve_nodate}. Overall, there are a tons of analogous applications that are commercially available nowadays. Nevertheless, they do not offer the high-quality of visualization (e.g., degree flowchart, curriculum sheet, etc.) as this project intended to provide. That is to say, instead of dragging and dropping courses on the interactive interface, students must manually search or enter the course information to the planner. This requires them to familiarize themselves with the degree requirements, which is challenging, especially for freshman students. In fact, these applications focus on degree auditing rather than solely planning; henceforth, they may not support the user-friendly interfaces. Another key point is that they are not applicable specifically to UTA degree planner, which can be implemented practically at campus-wide level.